Statement-level AST-based Clone Detection in Java using Resolved Symbols

### 2019-11-06 benevol/paper.tex
Updates from Overleaf

@@

@@

\subsection{Building the clone graph}\label{sec:buildingclonegraph}
Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following it.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to efficiently find out whether a statement is cloned with another. %An example of such a graph is displayed in Figure~\ref{fig:clonegraphsimple}.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CloneGraphCode}
  \caption{CloneRefactor extracts statements and declarations from source code.}
  \label{fig:clonegraph}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=1\columnwidth]{img/CodeGraphExample}
  \caption{Example of a clone graph built by CloneRefactor.}
  \label{fig:clonegraph2}
\end{figure}

@@

\subsubsection{Removing redundant clone classes}\label{sec:conceptualremovingredundant}
The clone detection method used by CloneRefactor can, for various reasons, result in redundant clone classes. After the insertion of each newly detected clone, we check whether it is redundant and/or any of the existent clones has become redundant by adding this clone. A clone is redundant if it is a subset of another clone. We define the subset relation between clones as follows:

\begin{equation}\label{eq:subset}
C_1 \subseteq C_2 := \forall (i_1 \in C_1) \text{ } \exists (i_2 \in C_2) \text{ } F i_1 = F i_2 \wedge R i_1 \subseteq R i_2
\end{equation} % Right symbol for definition

Where \textit{C} refers to a clone class (a set of clone instances), \textit{i} refers to a clone instance, \textit{F} is the file in which a clone instance is located and \textit{R} is the range of tokens that a clone instance spans. For each clone found, we remove all existing clones that are a subset of the found clone:

\begin{equation}\label{eq:removeall}
S_{after} = S_{before} \setminus \{C_{existing} \subseteq C_{new}\text{ }|\text{ }C_{existing} \in S_{before}\}
\end{equation}

Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after removing all subsets of the added clone.

We should not add the new clone to our list of clones if its a subset of an existing clone. Because of that, we check for each clone added whether there exists a clone class of which the found clone class is a subset:

\begin{equation}\label{eq:removeexisting}
\{C_{new} \subseteq C_{existing}\text{ }|\text{ }C_{existing} \in S\} = \emptyset \Rightarrow S_{after} = S \cup C_{new}
\end{equation}

Where \textit{$S_{before}$} is the clone class collection containing all clones that are found up in until this point, \textit{$C_{new}$} is the clone class that was just found and \textit{$S_{after}$} is the clone class collection after optionally adding the newly found clone. If the newly added clone is a subset of an existing clone, we do not add it to the set of clone classes. This way we avoid redundant clone classes being detected by CloneRefactor.

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=1\textwidth]{img/CodeGraphExample}
  \caption{Example of a clone graph built by CloneRefactor.}
  \label{fig:clonegraph2}
\end{figure*}

@@

\begin{figure*}
  \centering
  \includegraphics[width=1\textwidth]{img/CloneGraphCode}
  \caption{CloneRefactor extracts statements and declarations from source code.}
  \label{fig:clonegraph}
\end{figure*}

@@

\subsection{Building the clone graph}\label{sec:buildingclonegraph}
Building the clone graph consists of walking the AST in-order for each declaration and statement. For each declaration/statement found, we map the following relations:
\begin{itemize}
  \item The declaration/statement preceding it.
  \item The declaration/statement following it.
  \item The last \textbf{preceding} declaration/statement with which it is cloned.
\end{itemize}
We do not create a separate graph for each class file, so the statement/declaration preceding or following could be in a different file. While mapping these relations, we maintain a hashed map containing the last occurrence of each unique statement. This map is used to efficiently find out whether a statement is cloned with another. An example of such a graph is displayed in Figure~\ref{fig:clonegraph2}.

@@

@@

@@

\section{Results}
To compare the difference in detected clones when contextual information is considered, we
